---
title: "American Community Survey Exercise"
author: "Karlie Schwartzwald"
date: '2022-06-24'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/karli/OneDrive/Documents/Data Science/DSC520_Stats_for_DS/DSC520/dsc520/')
```

```{r load, include=FALSE}
# Load ggplot Library 
library(ggplot2)
theme_set(theme_minimal())
# Load the CSV file
survey_df <- read.csv("data/acs-14-1yr-s0201.csv")
```

### 1. What are the elements in your data (including the categories and data types)?

The categories of our data are ID (string), ID2 (integer), Geography (string), PopGroupID (integer), POPGROUP.display.label (string), RacesReported (integer), HSdegree (float), and Bachdegree (float).

### 2. Please provide the output from the following functions: str(); nrow(); ncol()

```{r}
str(survey_df)
nrow(survey_df)
ncol(survey_df)
```

### 3. Create a Histogram of the HSDegree variable using the ggplot2 package.

#### - Set a bin size for the Histogram.

#### - Include a Title and appropriate X/Y axis labels on your Histogram Plot.

  Knitting below:

```{r}

ggplot(survey_df, aes(HSDegree)) + ggtitle("Histogram of the Percentage of Population with High School Degree") + xlab("Percentage with HS Degree") + ylab("Frequency") + geom_histogram(aes(y = ..density..), binwidth = 0.5)
```

### 4. Answer the following questions based on the Histogram produced:

#### - Based on what you see in this histogram, is the data distribution unimodal?

Yes, the distribution is unimodal.

#### - Is it approximately symmetrical?

No, it is not symmetrical.

#### - Is it approximately bell-shaped?

Yes, it is approximately bell-shaped.

#### - Is it approximately normal?

No, it is not normal.

#### - If not normal, is the distribution skewed? If so, in which direction?

It is skewed in the negative direction.

#### - Include a normal curve to the Histogram that you plotted.

#### - Explain whether a normal distribution can accurately be used as a model for this data.

No we would need to use a skewed distribution.

```{r}
ggplot(survey_df, aes(HSDegree)) + ggtitle("Histogram of the Percentage of Population with High School Degree") + xlab("Percentage with HS Degree") + ylab("Frequency") + geom_histogram(aes(y = ..density..), binwidth = 0.5) + stat_function(fun = dnorm, colour = "red", args = list(mean=mean(survey_df$HSDegree, na.rm = TRUE), sd=sd(survey_df$HSDegree, na.rm = TRUE)), size = 1)
```

### 5. Create a Probability Plot of the HSDegree variable.

```{r}
qplot(sample = survey_df$HSDegree, stat="qq")
```

### 6. Answer the following questions based on the Probability Plot:

#### Based on what you see in this probability plot, is the distribution approximately normal? Explain how you know.

No, if it were normal there would be straight diagonal line instead of a curved one.

#### If not normal, is the distribution skewed? If so, in which direction? Explain how you know.

The distribution is negatively skewed. You can see that the line is concave down.

### 7. Now that you have looked at this data visually for normality, you will now quantify normality with numbers using the stat.desc() function. Include a screen capture of the results produced.

```{r}
library(pastecs)
stat.desc(survey_df$HSDegree, norm = TRUE)
```
### 8. In several sentences provide an explanation of the result produced for skew, kurtosis, and z-scores. In addition, explain how a change in the sample size may change your explanation?

With a skew value less than negative 1, we can consider this distribution significantly skewed in the negative direction and thus not normal.
a Kurtosis value above 1 is considered too pointy to be normal.
Thus our distributions is nonnormal.
Skew and Kurtosis can be used to calculate z-scores.
A larger sample size would result in a smaller standard error, and thus we would need a higher threshold of z-score.