---
title: "assignment_00_SchwartzwaldKarlie"
author: "Karlie Schwartzwald"
date: '2022-06-15'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Assignment: ASSIGNMENT 0

# Name: Schwartzwald, Karlie

# Date: 2022-06-06

# Basics


## Add 8 and 5
```{r}
8 + 5
```

## Subtract 6 from 22
```{r}
22 - 6
```

## Multiply 6 by 7
```{r}
6 * 7
```

## Add 4 to 6 and divide the result by 2
```{r}
(4+6)/2
```

## Compute 5 modulo 2
```{r}
5 %% 2
```

## Assign the value 82 to the variable x
## Print x
```{r}
x <- 82
x
```

## Assign the value 41 to the variable y
## Print y
```{r}
y <- 41
y
```

## Assign the output of x + y to the variable z
## Print z
```{r}
z <- x + y
z
```

## Assign the string value "DSC520" to the variable class_name
## Print the value of class_name
```{r}
class_name <- "DSC520"
class_name
```

## Assign the string value of TRUE to the variable is_good
## Print the value of is_good
```{r}
is_good <- TRUE
```

## Check the class of the variable is_good using the `class()` function
```{r}
class(is_good)
```

## Check the class of the variable z using the `class()` function
```{r}
class(z)
```

## Check the class of the variable class_name using the class() function
```{r}
class(class_name)
```
