---
title: "Assignment 03"
author: "Karlie Schwartzwald"
date: '2022-06-23'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:/Users/karli/OneDrive/Documents/Data Science/DSC520_Stats_for_DS/DSC520/dsc520')
```
## Load the ggplot2 package
```{r load}
library(ggplot2)
theme_set(theme_minimal())
```
## Set the working directory to the root of your DSC 520 directory
**Note: This was done during the 'setup' chunk since this is an Rmarkdown file.**
```{r}
getwd()
```
## Load the `data/r4ds/heights.csv` to
```{r}
heights_df <- read.csv("data/r4ds/heights.csv")
```
# https://ggplot2.tidyverse.org/reference/geom_point.html
## Using `geom_point()` create three scatterplots for
## `height` vs. `earn`
```{r}
ggplot(heights_df, aes(x=height, y=earn)) + geom_point()
```
## `age` vs. `earn`
```{r}
ggplot(heights_df, aes(x=age, y=earn)) + geom_point()
```
## `ed` vs. `earn`
```{r}
ggplot(heights_df, aes(x=ed, y=earn)) + geom_point()
```
## Re-create the three scatterplots and add a regression trend line using
## the `geom_smooth()` function
## `height` vs. `earn`
```{r}
ggplot(heights_df, aes(x=height, y=earn)) + geom_point() + geom_smooth()
```
## `age` vs. `earn`
```{r}
ggplot(heights_df, aes(x=age, y=earn)) + geom_point() + geom_smooth()
```
## `ed` vs. `earn`
```{r}
ggplot(heights_df, aes(x=ed, y=earn)) + geom_point() + geom_smooth()
```
## Create a scatterplot of `height`` vs. `earn`.  Use `sex` as the `col` (color) attribute
```{r}
ggplot(heights_df, aes(x=height, y=earn, col=sex)) + geom_point()
```
## Using `ggtitle()`, `xlab()`, and `ylab()` to add a title, x label, and y label to the previous plot
## Title: Height vs. Earnings
## X label: Height (Inches)
## Y Label: Earnings (Dollars)
```{r}
ggplot(heights_df, aes(x=height, y=earn, col=sex)) + ggtitle("Height vs. Earnings") + xlab("Height (Inches)") + ylab("Earnings (Dollars)") + geom_point()
```
# https://ggplot2.tidyverse.org/reference/geom_histogram.html
## Create a histogram of the `earn` variable using `geom_histogram()`
```{r}
ggplot(heights_df, aes(earn)) + geom_histogram()
```
## Create a histogram of the `earn` variable using `geom_histogram()`
## Use 10 bins
```{r}
ggplot(heights_df, aes(earn)) + geom_histogram(bins = 10)
```
# https://ggplot2.tidyverse.org/reference/geom_density.html
## Create a kernel density plot of `earn` using `geom_density()`
```{r}
ggplot(heights_df, aes(earn)) +  geom_density()
```