---
title: "Assignment Week 5"
author: "Karlie Schwartzwald"
date: '2022-07-08'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(magrittr)
```

First, I open the 2014 American Community Survey data:

## 1. Dplyr package

```{r  housing_import}
library(readxl)
setwd('C:/Users/karli/OneDrive/Documents/Data_Science/DSC520_Stats_for_DS')
week_6_housing <- read_excel("week-6-housing.xlsx")
colnames(week_6_housing)[2] <- "Sale_Price"
housing_complete <- na.omit(week_6_housing)
head(housing_complete)
```
#### Using the GroupBy function:

```{r  GroupBy}
housing_complete %>%
  group_by(bedrooms) %>%
  summarize(mean(square_feet_total_living))
```
#### Using the Summarize function:

```{r  Summarize}
housing_complete %>%
 group_by(building_grade) %>%
 summarize(mean(Sale_Price))
```
#### Using the Mutate function:

```{r  Mutate}
housing_complete %>% 
  select(Sale_Price, sq_ft_lot) %>%
  mutate(Sale_Price/sq_ft_lot)
```
#### Using the Filter function:

```{r  Filter}
housing_complete %>% filter_("year_renovated != 0")
```
#### Using the Select function:

```{r  Select}
housing_complete %>%
  select_('Sale_Price')
```
#### Using the Arrange function:

```{r  Arrange}
housing_complete %>%
  group_by(bedrooms) %>%
  summarize(avgprice=mean(Sale_Price)) %>%
  arrange(avgprice)
```

## 2. Purrr Package

#### Using the keep function:
```{r  keep}
# You could use zip_n, keep, discard, compact, etc.
library(purrr)
expensive_sales <- housing_complete$Sale_Price %>%
  keep(~{mean(.x)>600000})
head(expensive_sales)
```

#### Using the  function:
```{r }
# You could use zip_n, keep, discard, compact, etc.
complete_sale_price <- housing_complete$Sale_Price %>%
  compact()
head(complete_sale_price)
```

## 3. cbind and rbind

#### cbind
```{r cbind}
bathrooms <- cbind('Full Bath'=week_6_housing$bath_full_count, '3/4 Bath'=week_6_housing$bath_3qtr_count, '1/2 Bath'=week_6_housing$bath_half_count)
head(bathrooms)
```

#### rbind
```{r rbind}
cheap_sales <- week_6_housing %>%
  filter(Sale_Price<600000) %>%
  cbind()
head(cheap_sales)
```

## 4. Split a string, then concatenate the results back together
```{r concatenate}
library(stringr)

# create string
string1 <- "I need to split a string~ I will split based on the tilde~ Hopefully there will be enough tilde to split on~ Testing now."
print(string1)

# Split String
split_string1 <- str_split(string=string1,pattern='~')
print(split_string1)
paste(unlist(split_string1), sep = " ", collapse = "~")
```
